Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-22 writeups/dissertation/dissertation.tex
foo

The majority of the modeling and analysis was done with the R statistical computing environment \parencite{RCoreTeam2014}, and the data.table \parencite{Dowle2014} and ggplot2 \parencite{Wickham2009} packages.

>>>>

The majority of the modeling and analysis was done with the R statistical computing environment \parencite{RCoreTeam2014} and two important R packages:
data.table \parencite{Dowle2014} was leveraged to implement the models efficiently, and ggplot2 \parencite{Wickham2009} was used to produce the visualizations.
